Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-19 paper/paper_acm.tex
adding brackets to ease the reading
typo
repetition and typos

\begin{prop}
  A type $F$ is $\Type_{n+1}$ is separated if, and only if all its
  path types are $n$-modal, ie
  \begin{mymath}[-0.3em]\prod_{x,y:F}~\modal_n(x=y) = (x=y).\end{mymath}%
\end{prop}

@@

In topos-theoretic words, it means that given a map $\sum_{e:E}
\chi\, e\to F$, one can
extend it uniquely in $\tilde f:E \to F$.

@@

For a given induction step, the sheafification is defined in two
steps ; the first one (section~\ref{ssec:from-type-separated}) construct, for any $T:\Type_{n+1}$ a separated
type $\separated T$, and the second one
(section~\ref{ssec:separated-to-sheaf}) construct a sheaf given any
separated type.
% %
% \begin{enumerate}[(i)]
% \item {\em separation:} From any $T$ in $\Type_{n+1}$, we construct
%   its {\em free} separated object $\separated T$ by ``removing'' what
%   prevents $T$ from being a sheaf.
% \item {\em completion:} We add what is missing for the free 
%   separated type to be a sheaf by using closure in a sheaf.
% \end{enumerate}

>>>>

\begin{prop}
  A type $F$ is $\Type_{n+1}$ is separated if, and only if all its
  path types are $n$-modal, ie
  \begin{mymath}[-0.3em]\prod_{x,y:F}~\left( \modal_n(x=y) \right) = (x=y).\end{mymath}%
\end{prop}

@@

In topos-theoretic words, it means that given a map $f : \sum_{e:E}
\chi\, e\to F$, one can
extend it uniquely to $\tilde f:E \to F$.

@@

For a given induction step, the sheafification is defined in two
phases; the first one (section~\ref{ssec:from-type-separated}) constructs, for any $T:\Type_{n+1}$ a separated
type $\separated T$, and the second one
(section~\ref{ssec:separated-to-sheaf}) constructs a sheaf given any
separated type.
% %
% \begin{enumerate}[(i)]
% \item {\em separation:} From any $T$ in $\Type_{n+1}$, we construct
%   its {\em free} separated object $\separated T$ by ``removing'' what
%   prevents $T$ from being a sheaf.
% \item {\em completion:} We add what is missing for the free 
%   separated type to be a sheaf by using closure in a sheaf.
% \end{enumerate}
